### 2010-03-07 pkg/yuimadocs/inst/doc/yuima_5.Rnw
minor addition on documentation
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/yuima@64 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

>>>>

\subsection{Technical Details}
2010/03/07: Hideitsu Hino wrote\\
[TBC: Description about ml.ql function. It's possible options. Optim
function equipped with R which uses ``Nelder-Mead method'' for
likelihood maximization. By specifying method=''Newton'', we can use
Newton method for likelihood maximization.]

[TBC: Description about adaBayes function. It's possible options. MCMC.]

[TBC: Return value format of ml.ql and adaBayes. It is in the same form
to the return value of ``mle'' function. That is, we can apply
``confint'' to get their confidence intervals.]
